DATA 621 - Business Analytics and Data Mining

### 2020-10-30 HW3/HW3-Group2.Rmd
spelling

We can make some initial observaations. The data set has complete cases, thus, 
there is no need for imputation. Based on some common summary statistics, there
are more observations where the crime rate is below the median. It is already 
apparent that some of the predictors varies depending the crime rate. For
instance, there is a noticeable difference in the means of `age`, `lstat`,
`rad`, and `zn` between the crime rate groups.

@@

## Model 3
For model 3, we chose very little data manipulation, as there may be valuable 
information in the outliers. A reasonable model may be able to extract something
from `chas`. Some variables, such as `chas` and `rad`, an index of accessibility,
are converted to a factor. Additionally, while `rad` may have an ordering, it
will be converted to a normal factor, as ordered factors are processed via
orthogonal polynoial regression, which is out of the scope of this class. Given
that there are now two factors in the predictors, we require creation of dummy 
variables. Lastly, the **labels** of `target` will be changed from integer to 
character for compliance with some of R's naming conventions.  Based on the 
definitions, 0 will be mapped to *Below* and 1 to *Above*.

@@

# Model 1: Capture the indices for Model 3 then remove the uneeded column
tstIDX <- test_df$id
crime_df <- subset(crime_df, select = -id)
train_df <- subset(train_df, select = -id)
test_df <- subset(test_df, select = -id)
```

@@

Considering *all* interactions would be foolhardy. Given the need for dummy
variables, there will 19 predictors and \(_{19}C_2 = 171\) possible pairs---too
much. Therefore, intentional selection of pairs is required.

@@

A number of variables fell out of the model, such as `chas`, `dis`, and `zn` 
among others. The remaining predictors are all significant, at least at the 10% 
level, except for `rad.24`. However, from the last trace of the stepping routine 
shown below, removing it would ***drastically*** reduce the models performance.

>>>>

We can make some initial observations. The data set has complete cases, thus, 
there is no need for imputation. Based on some common summary statistics, there
are more observations where the crime rate is below the median. It is already 
apparent that some of the predictors varies depending the crime rate. For
instance, there is a noticeable difference in the means of `age`, `lstat`,
`rad`, and `zn` between the crime rate groups.

@@

## Model 3
For model 3, we chose very little data manipulation, as there may be valuable 
information in the outliers. A reasonable model may be able to extract something
from `chas`. Some variables, such as `chas` and `rad`, an index of accessibility,
are converted to a factor. Additionally, while `rad` may have an ordering, it
will be converted to a normal factor, as ordered factors are processed via
orthogonal polynomial regression, which is out of the scope of this class. Given
that there are now two factors in the predictors, we require creation of dummy 
variables. Lastly, the **labels** of `target` will be changed from integer to 
character for compliance with some of R's naming conventions.  Based on the 
definitions, 0 will be mapped to *Below* and 1 to *Above*.

@@

# Model 1: Capture the indices for Model 3 then remove the unneeded column
tstIDX <- test_df$id
crime_df <- subset(crime_df, select = -id)
train_df <- subset(train_df, select = -id)
test_df <- subset(test_df, select = -id)
```

@@

Considering *all* interactions would be foolhardy. Given the need for dummy
variables, there will 19 predictors and \(_{19}C_2 = 171\) possible pairs---too
many! Therefore, intentional selection of pairs is required.

@@

A number of variables fell out of the model, such as `chas`, `dis`, and `zn` 
among others. The remaining predictors are all significant, at least at the 10% 
level, except for `rad.24`. However, from the last trace of the stepping routine 
shown below, removing it would ***drastically*** reduce the model's performance.
